---
title: "Case Study"
author: Lesi He
output: html_document
---

```{r, message = FALSE}
library(tidyverse)
library(p8105.datasets)
library(leaflet)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
```


## load a dataset
```{r}
data("nyc_airbnb")
```


Possible Questions:
* How many rentals are there? Of what type? In what places?
* Is price correlated with review score?
* Which neighborhood is most popular? Most expensive?
* Which neighborhood has the highest reviews?
*Is availability related to price/
* Is room type related to neighborhood?
* Is length of stay related to neighborhood group?


```{r}
nyc_airbnb = 
  nyc_airbnb %>% 
  mutate(stars = review_scores_location / 2) %>% 
  rename(borough = neighbourhood_group)
```



Let's try to count things:
```{r}
nyc_airbnb %>% 
  #janitor::tabyl(borough, room_type)
  count(borough, room_type) %>% 
  pivot_wider(
    names_from = room_type,
    values_from = n
  )
```


how did neighborhood relate to price?
```{r}
nyc_airbnb %>% 
  #janitor::tabyl(borough, stars)
  count(borough, price) %>% 
  pivot_wider(
    names_from = price,
    values_from = n
  )
```


price and room-type
```{r}
nyc_airbnb %>% 
  ggplot(aes(x = stars, y = price)) + 
  geom_point() + 
  facet_grid(. ~ room_type)
```


price and neighborhood
```{r}
nyc_airbnb %>% 
  filter(borough == "Manhattan") %>% 
  group_by(neighbourhood) %>% 
  summarize(mean_price = mean(price, na.rm = TRUE)) %>% 
  arrange(mean_price)

nyc_airbnb %>% 
  filter(borough == "Manhattan",
         price <= 1000) %>% 
  mutate(neighbourhood = 
           fct_reorder(neighbourhood, price)) %>% 
  ggplot(aes(x = neighbourhood, y = price)) + 
  geom_boxplot() + 
  coord_flip() +
facet_grid(. ~ room_type)
```

price and location
```{r}
nyc_airbnb %>% 
  filter(price < 500) %>% 
  #randomly select n number of data point
  sample_n(5000) %>%  
  ggplot(aes(x = lat, y = long, color = price)) +
  geom_point(alpha = .5)
```


## retry leaflet
https://rstudio.github.io/leaflet/
```{r}
pal = colorNumeric("viridis", NULL)
nyc_airbnb %>% 
  filter(price < 500) %>% 
  sample_n(1000) %>% 
  leaflet() %>% 
  addProviderTiles(providers$CartoDB.Positron) %>% 
  addCircleMarkers(~lat, ~long, radius = 1, color = ~pal(price))
```





